An Authoritative Adventure

### 2021-12-24 article.tex
Added a DndQuote document command, using a similar mechanism to the spell/item header
Added example of changing number of columns in dndlongtable

@@

>>>>

\subsection{Quotes}
\DndQuote%
  {``Sometimes, what you need and what you}
  {want turn out to be the same thing: An uplifting quote.''}
  {The Adventurer}

@@

Since |dndlongtable| accepts column definitions in the standard |tabular|
format, alternate numbers of columns can be defined by passing an optional
parameter. For example, using:

\begin{lstlisting}[basicstyle=\ttfamily\small]
\begin{dndlongtable}[c p{0.66\linewidth} p{0.1\linewidth}]
\end{lstlisting}

Yields a three-column table:

\begin{dndlongtable}[c p{0.65\linewidth} p{0.12\linewidth}]
    \textbf{d100} & \textbf{Result} & \textbf{GP} \\
    1-2 & You win a magic item or an expensive piece of classic artwork. & 100 gp \\
    ... & & \\
    100 & You win a magic item or an expensive piece of classic artwork. & 1000 gp \\
\end{dndlongtable}
